Tutorial_2a

### 2024-12-13 Tutorial_2a.Rmd
update 2a and 2b html

The shape of the prior predictive distribution for 1 bin looks as expected (compare with Figure 16 (row F) in the supplementary material): hazard values below .5 are more likely than hazard values above .5.

>>>>

The shape of the prior predictive distribution for 1 bin looks as expected (compare with Supplementary Figure 2 (row F) in the Supplemental Material): hazard values below .5 are more likely than hazard values above .5.
